---
title: "Get Started With cccapi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started With cccapi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| include = FALSE

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette will demonstrate the basic functionality of cccapi and provides 
example code to work with SVG and MOL files.

## Installing and loading cccapi

cccapi can be installed from GitHub with the following command:

```{r install}
#| eval = FALSE
install.packages("remotes")
remotes::install_github("ZeroPM-H2020/cccapi")
```

The package can be loaded like any other R package: 

```{r setup}
library(cccapi)
```


## Searching for "atrazine"

You might want to search for a substance, say 
[atrazine](https://en.wikipedia.org/wiki/Atrazine). This can be done with the 
`get_search()` function. 

```{r search}
atz_src <- get_search("atrazine")

str(atz_src)
```

The returned list contains, among other things, the CAS Registry Number 
associated with atrazine in `atz_src$results$rn`. This can be used to 
retrieve more details.


## Atrazine details

The details for the atrazine entry can be retrieved using the `get_detail()`
function.

```{r detail}
atz_dtl <- get_detail(atz_src$results$rn)

str(atz_dtl)
```

We now have access to the SVG file and know that a MOL file exists!


## Saving and looking at SVG image files

The downloaded picture can saved with the `writeLines()` function. 

```{r svg1}
writeLines(text = atz_dtl$image, con = "atrazine.svg")
```

The SVG can also be read with, for example, the `image_read_svg()` function of 
the [magick](https://cran.r-project.org/web/packages/magick/index.html) 
package. This function requires the 
[rsvg](https://cran.r-project.org/web/packages/rsvg/index.html) package. 

```{r svg2}
atz_img <- magick::image_read_svg(atz_dtl$image)

atz_img
```


## Writing MOL files

When a MOL file is available, it can be downloaded with the `get_export()`
function. To write the MOL file, the `writeLines()` function can be used.

```{r mol}
atz_mol <- get_export(atz_src$results$rn)

str(atz_mol)

writeLines(text = atz_mol, con = "atrazine.mol")

readLines(con = "atrazine.mol")
```

